A significance test in forward stepwise regression

### 2014-03-20 paper/paper.tex
Paper: simulation section exposition

@@

\todo Clean up and reorganize \\
\todo Write a little more exposition \\
\todo Compare to AIC and other classical stopping rules? \\

\begin{figure}[h]
\begin{center}
\subfigure[Gaussian design]{
\label{fig:smallgauss}
\includegraphics[width=0.5\textwidth]{../figs/gaussian_size1_n100_p200_g200_k10_lower1p8_upper1p9.pdf}}
\hspace{-15pt}
\subfigure[Categorical design]{
\label{fig:smallcat}
\includegraphics[width=0.5\textwidth]{../figs/gaussian_size1_n100_p200_g200_k10_lower1p8_upper1p9_corr0p1.pdf}}
\caption{\small \it The left panel shows results of a simulation with
  an independent Gaussian design matrix and a signal vector having
  three groups with non-zero coefficients of sizes one, two, and
  three, and seven groups of noise variables with sizes varying from
  one to ten, for a total of 30 variables. For the right panel we
  repeated this setup, but group sizes corresponded to levels of
  categorical variables. The groups of size one were increased to two,
so there are 10 categorical variables with a total of 32 levels.}
\end{center}
\end{figure}

@@

\subsection{Real data example}
\todo Sanity check my analysis \\
\todo For rare mutations try binary wildtype/non-wt? \\
\todo Finish writing section \\

>>>>

\todo Complete this section

@@

\todo Compare to AIC and other classical stopping rules? \\

We performed simulations with several classes of design matrices including
Gaussian, categorical, and categorical from a real data set. Gaussian
design matrices are generated either independently or with some global
correlation $\rho > 0$ between all pairs of columns. Categorical matrices
were generated by first choosing a vector of probabilities for a given
variable from a Dirichlet prior, and then sampling category levels with
that vector of probabilities. Resampling was used to ensure the minimum
number of observations in any level was at least five. Finally, categorical
varables were encoded as groups of 0-1 vectors using the full encoding.
The categorical data matrices from real data are described in
Section~\ref{sec:hiv}

Since we are interested in variable selection we generate signals with
nonzero coefficients on the scale of $\gamma := \sqrt{2 \log(p)/n}$.
(\todo Cite some paper on support recovery?). Coefficients within a
nonzero group have roughly the same magnitude, and the magnitudes for
each nonzero group range from a lower limit times $\gamma$ to an upper
limit times $\gamma$. In plots, the limits are listed next to ``beta:''
and the numbers in parentheses are the largest and smallest 2-norms of
nonzero coefficient groups respectively. Each plot also displays the
number of observations or rows, $n$, the number of columns, $p$, the
number of groups, $g$, and the largest and smallest group sizes in
parentheses if the groups are not all size 1. The number of nonzero
groups, $k$, is also displayed via inward-facing tick marks on the
horizontal axes. The proportion of truly
nonzero groups recovered in the first $k$ steps is denoted $k$-SP,
where recall $k$ is the number of truly nonzero groups.

Finally, most of the plots below show the following information. The
horizontal axis is the step index for forward stepwise. The dashed
line shows the proportion of iterations where a truly nonzero variable
was added to the model at that step. Solid verticle lines show the
middle 50\% of p-values calculated at that step, with red calculated
on a null model with no nonzero groups, blue calculated on the non-null
model, and green calculated on the non-null model from the usual
$\chi^2$ significance test.
The points in these lines are the average p-value at that step, and
the triangles above and below show the 95\% and 5\% quantiles.

\begin{figure}[h]
\begin{center}
\subfigure[Gaussian design]{
\label{fig:smallgauss}
\includegraphics[width=0.5\textwidth]{../figs/gaussian_n100_p200_g200_k5_lower1pt5_upper2_corr0pt2_noisecorr0pt1.pdf}}
\hspace{-15pt}
\subfigure[Categorical design]{
\label{fig:smallcat}
\includegraphics[width=0.5\textwidth]{../figs/categorical_n100_p100_g20_k4_lower4_upper5.pdf}}
\caption{\small \it The left panel shows results for Gaussian design
matrices with equicorrelation $\rho=0.2$ and equicorrelated noise with
correlation 0.1. The right panel shows results for categorical matrices
with all categories having 5 levels.}
\end{center}
\end{figure}

@@

\subsection{Real data example}
\label{sec:hiv}
\todo Sanity check my analysis \\
\todo For rare mutations try binary wildtype/non-wt? \\
\todo Finish writing section \\
